Real Estate

### 2022-10-26 src/real_estate.Rmd

@@

```{r}
# combine real estate and demographic data by cbsa
MSA_demo_data <- MSA_demo_data %>% 
  left_join(MSA_realEstate_data)
```

>>>>

```{r}
# select columns in demographic data
MSA_demo_data <- MSA_demo_data %>% 
  clean_names() %>% 
  select(cbsa, msa, state, employment_yo_y21_22, pop_percent_change20_21, median_income_usd_2021, house_price_2021, median_tax_usd)
```

@@

```{r}
# combine real estate and demographic data by cbsa
MSA_realEstate_data <- MSA_demo_data %>% 
  left_join(MSA_realEstate_data)
```
